Probability

### 2016-04-22 prob.tex
prob.tex "\subsection{Quantum Probability Spaces}" update comments...

We now formalize a \emph{quantum probability space} as follows~\cite{BirkhoffVonNeumann1936,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}.
We first assume an ambient Hilbert space~$\Hilb$ and define the
set of events $\qevents$ as all \emph{projections} on~$\Hilb$.
Each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\mu_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $E\in\qevents$ as follows\footnote{Recently, people extend the domain of $\mu_{\psi}$ to all operators~$\mathcal{A}$
on $\Hilb$ and consider $\mu_{\psi}:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
When an operator $A\in\mathcal{A}$ is Hermitian, $\mu_{\psi}\left(A\right)$
is the expectation value of $A$. We does not take this approach because
we want to focus only on probability. }: 
\begin{equation}
\mu_{\psi}(E)= \ip{\psi}{E\psi} \label{eq:Born}
\end{equation}
Similarly to the classical case, this probability measure must satisfy:
\begin{itemize}
\item $\mu(\mathbb{1})=1$, and 
\item for a collection of pairwise orthogonal $E_i$, we have
  $\mu(\sum_i E_i) = \sum_i \mu(E_i)$.

\yutsung{Claim: If $\sum_{i}\proj{\psi_{i}}$ is a projection, then
they are orthogonal. \\
Proof: If $\sum_{i}\proj{\psi_{i}}$ is a projection, then 
\begin{eqnarray*}
\ket{\psi_{j}} & = & \left(\sum_{i}\proj{\psi_{i}}\right)\ket{\psi_{j}}\\
 & = & \sum_{i}\ket{\psi_{i}}\ip{\psi_{i}}{\psi_{j}}
\end{eqnarray*}
Therefore, we have 
\begin{eqnarray*}
0 & = & \sum_{i\ne j}\ket{\psi_{i}}\ip{\psi_{i}}{\psi_{j}}
\end{eqnarray*}
} 
\end{itemize}

>>>>

We now formalize a \emph{quantum probability space} as follows~\cite{BirkhoffVonNeumann1936,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}.
We first assume an ambient Hilbert space~$\Hilb$ and define the
set of events $\qevents$ as all \emph{projections} on~$\Hilb$.
Each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\mu_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $E\in\qevents$ as follows\footnote{Recently, people extend the domain of $\mu_{\psi}$ to all operators~$\mathcal{A}$
on $\Hilb$ and consider $\mu_{\psi}:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
When an operator $A\in\mathcal{A}$ is Hermitian, $\mu_{\psi}\left(A\right)$
is the expectation value of $A$. We does not take this approach because
we want to focus only on probability. }: 
\begin{equation}
\mu_{\psi}(E)= \ip{\psi}{E\psi} \label{eq:Born}
\end{equation}
Similarly to the classical case, this probability measure must satisfy:
\begin{itemize}
\item $\mu(\mathbb{1})=1$, and 
\item for a collection of pairwise orthogonal $E_i$, we have
  $\mu(\sum_i E_i) = \sum_i \mu(E_i)$. 
\end{itemize}
\yutsung{There are three ways to charactize a quantum probability:
\begin{enumerate}
\item The above two conditions as Gleason did.
\item As a linear functional on a {*} algebra.
\item As induced by a state vector by the Born rule (\ref{eq:Born}).
\end{enumerate}
According to equation (37) in section 4 Quantum Probability in \cite{Maassen2010},
the equalivance between 1. and 2. only hold for $d\ge3$ because of
Gleason' theorem. Therefore, it seems hard to get insight for how
to handle Gleason's theorem by {*}-algebra formulism...

The equalivance between 2. and 3. can be found
in Proposition 4.1.1 in \cite{Swart2013}. Notice that this proposition
holds for every dimension... So it is not exactly Gleason's theorem,
or at least not the main part of the Gleason's theorem...}
